\thetitle

### 2008-08-30 paper/paper.tex
paper: macro for author and title; bib: macro plus tidying
darcs-hash:20080830065529-d98fc-73bb4fcc53a3cc2f72f22b9a0748578496987489.gz

\usepackage{color}
\usepackage[colorlinks,pdftitle={dus},pdfauthor={James McKinna and Eelis van der Weegen}]{hyperref}

@@

\title{A Machine-checked Proof of the Average-case Complexity of Quicksort in Coq}

@@

\author{James McKinna and Eelis van der Weegen}

>>>>

\newcommand{\theauthors}{James McKinna and Eelis van der Weegen}
\newcommand{\thetitle}{A Machine-checked Proof of the Average-case Complexity of Quicksort in Coq}

\usepackage{color}
\usepackage[colorlinks,pdftitle={dus},pdfauthor=\theauthors]{hyperref}

@@

\title{\thetitle}

@@

\author{\theauthors}
